Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-11 bbbq_article.tex
Add DRiPS, epitope fusion and all those other goodies for the discussion

@@

@@

DRIPs.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Elution studies}\label{subsec:elution_studies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Elution studies}

We assume that epitopes 
derived from TMHs are actually presented by MHC-I and MHC-II.
Our analysis (at subsection \ref{subsec:elution_studies}) 
finds that 1.4\% (for MHC-I) and 4.0% (for MHC-II) 
of the epitopes presented 
overlap with a TMH.
It is unsure if this a true finding or a false positive.
One source of noise would stem from imperfect predictions
by the topology prediction software used. 
We have counteracted this by using two different topology prediction
software and confirm these have similar results.
Two biological sources of noise
are defective ribosomal products (DRiPs) (\cite{yewdell1996defective}) 
and peptide fusion \cite{delong2016pathogenic},
two processes that both result in peptide fragments
that did not originate from genome directly.
Note however, that both elution studies have a
methodological bias caused by mass spectronomy,
as hydrophobic fragments are detected less 
by mass spectronomy \richel{Look up wording and ref in Bianchi et al 2017}.

\paragraph{\% epitopes overlapping with TMHs}

@@

\paragraph{Evolutionary conservation}

In our evolutionary experiment, we removed variations that were synonymous mutations (i.e.
resulted in the same amino acid, from a different genetic code) 
from our analysis.
There is evidence, however, that these synonymous mutations
do have an effect and may even be evolutionary selected 
for (\cite{hunt2009silent}).
As the possible effect of synonymous mutations is ignored by our
topology prediction software, we do so as well.
